\plaintitle

### 2017-06-17 papers/IoT2017/paper.tex
no message

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage[textsize=tiny, textwidth=1.3cm, disable]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}
\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
\newcommand{\Aron}[1]{\todo[color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Providing Privacy, Safety, and Security in IoT-Based Transactive Energy Systems}
\def\plainauthor{First Author, Second Author, Third Author}
\def\emptyauthor{}
\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid; smart grid; anonymity.}
\def\plaingeneralterms{Design, Human Factors, Reliability, Security} % TODO: revise

@@

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply.  It is hard, however, to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and \Abhishek{To what extent is
  this different that the information already known by the system
  operator? Is this more related to the ``real-time'' nature of
  transactive information?  Rather than aggregative total information
  which is available at the end of billing cycle today.} \Aron{Do we
  need to detail this in the abstract?}\Abhishek{we dont have to} the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes our secure and safe solution for
transactive microgrids, which enables consumers to trade energy
without sacrificing their privacy.  Our solution builds on distributed
ledgers, such as blockchains, and provides anonymity for
communication, bidding, and trading.
\end{abstract}

>>>>

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage[textsize=tiny, textwidth=1.3cm]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}
\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
\newcommand{\Aron}[1]{\todo[color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}
\newcommand{\Doug}[1]{\todo[color=red!40, linecolor=black!50]{\textbf{Doug}: #1}}

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Providing Privacy, Safety, and Security in IoT-Based Transactive Energy Systems using Distributed Ledgers}
\def\plainauthor{First Author, Second Author, Third Author}
\def\emptyauthor{}
\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid; smart grid; anonymity.}
\def\plaingeneralterms{Design, Human Factors, Reliability, Security} % TODO: revise

@@

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply. However, it is hard to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and \Abhishek{To what extent is
  this different that the information already known by the system
  operator? Is this more related to the ``real-time'' nature of
  transactive information?  Rather than aggregative total information
  which is available at the end of billing cycle today.} \Aron{Do we
  need to detail this in the abstract?}\Abhishek{we dont have to} the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes our secure and safe solution for
transactive microgrids, which enables consumers to trade energy
without sacrificing their privacy.  Our solution builds on distributed
ledgers, such as blockchains, and provides anonymity for
communication, bidding, and trading.
\end{abstract}

### 2017-06-17 papers/IoT2017/prelim.tex
no message

\subsubsection{Distributed Ledger}
This ledger permanently stores transactions that specify energy
trades, change regulatory policies for the microgrid, etc.  For
providing security and safety, it is crucial that transactions are
non-malleable, \emph{i.e.}, after a transaction has been recorded, it
cannot be modified or removed from the ledger.  To enhance fault
tolerance, however, the ledger should also be distributed.

>>>>

\subsubsection{Distributed Ledger}
This ledger permanently stores transactions that specify energy
trades, change regulatory policies for the microgrid, etc.  For
providing security and safety, it is crucial that transactions are
immutable, \emph{i.e.}, after a transaction has been recorded, it
cannot be modified or removed from the ledger.  To enhance fault
tolerance, however, the ledger should also be distributed.

### 2017-06-17 papers/IoT2017/solution.tex
no message

First, consider a prosumer who wishes to sell energy to another
prosumer, as shown in Figure~\ref{fig:sellFlow}. 
As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.

@@

\Doug{Abhishek, it seems like we might need a transition here since the previous paragraph seemed to wrap up the ``Overview of the Trading Process'' subsection above.  It's not clear how the rest of this text ties in with that discussion.  Perhaps we could use subsubsections to make these parts more distinct?}
\Aron{It did not wrap up. We have only discussed the process from the seller's perspective.}
Second, consider a prosumer who would like to buy energy from another prosumer.
Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.

>>>>

\subsubsection{Energy Selling Process}
Consider a prosumer who wishes to sell energy to another
prosumer, as shown in Figure~\ref{fig:sellFlow}. 
As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.

@@

\subsubsection{Energy Buying Process}
Consider a prosumer who would like to buy energy from another prosumer.
Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
